Screening Sinkhorn Algorithm for Regularized Optimal Transport

### 2019-05-21 tex/v3/section_3_algorithm.tex
update algo

In this spirit, let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
To keep only $n_b$-budget and $m_b$-budget of points, the parameters $\kappa$ and $\varepsilon$ satisfy ${\varepsilon^2}\kappa^{-1} = \xi_{n_b}$ and $\varepsilon^2\kappa = \zeta_{m_b}$. Hence 
\begin{equation}
\label{epsilon_kappa}
 \varepsilon = (\xi_{n_b}\zeta_{m_b})^{1/4} \text{ and } \kappa = \sqrt{\frac{\zeta_{m_b}}{\xi_{n_b}}}.
\end{equation}
Note that in one hand we have $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$ by construction. On the other hand, when $(n_b,m_b)$ tends to the full number budget of points $(n,m)$, the couple parameters $(\varepsilon, \kappa)$ converges to $(0,1)$. 
In Figure~\ref{fig:kappa_epsilon}, we plot these convergences, and hence in this case the approximate dual in problem \eqref{screen-sinkhorn} corresponds to the dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.

>>>>

In this spirit, let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
To keep only $n_b$-budget and $m_b$-budget of points, the parameters $\kappa$ and $\varepsilon$ satisfy ${\varepsilon^2}\kappa^{-1} = \xi_{n_b}$ and $\varepsilon^2\kappa = \zeta_{m_b}$. Hence 
\begin{equation}
\label{epsilon_kappa}
 \varepsilon = (\xi_{n_b}\zeta_{m_b})^{1/4} \text{ and } \kappa = \sqrt{\frac{\zeta_{m_b}}{\xi_{n_b}}}.
\end{equation}
Note that in one hand we have $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$ by construction. On the other hand, when $(n_b,m_b)$ tends to the full number budget of points $(n,m)$, the couple parameters $(\varepsilon, \kappa)$ converges to $(0,1)$. 
In Figure~\ref{fig:kappa_epsilon}, we plot these convergences, and hence the objective of approximate dual in problem \eqref{screen-sinkhorn} converges to the objective of dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
